Gafo-cc visuals

### 2024-02-28 analysis/gafo-cc-visuals.Rmd
run inward click model on cluster

```{r}
library(tidyverse)
library(ggpubr)
library(ggthemes)
library(tidyboot)
library(maps)
library(brms)
library(cowplot)
```

```{r}
data <- read_csv("../data/gafo-cc-clean-data.csv")%>%
  mutate(continent = ifelse(
    community %in% c("leipzig", "plymouth"), "Europe", 
    ifelse(
      community %in% c("akure", "hai||om", "khwe", "chimfunshi", "bandongo", "bayaka", "windhoek", "uganda"), "Africa",
      ifelse(community %in% c("stanford", "mexico", "buenos_aires"), "America",
             ifelse(community %in% c("india", "beijing", "turkey"), "Asia", "Oceania"))
    )
  ))%>%
  mutate(continent = factor(continent, levels = c("America", "Africa", "Europe", "Asia", "Oceania"), ordered = T))%>%
  mutate(community = recode(community,
                            akure = "Akure (Nigeria)",
                            leipzig = "Leipzig (Germany)",
                            `hai||om` = "Hai||om (Namibia)",
                            khwe = "Khwe (Namibia)",
                            windhoek = "Windhoek (Namibia)",
                            stanford = "Stanford (USA)",
                            chimfunshi = "Chimfunshi (Sambia)",
                            mexico = "Ocuilan (Mexico)",
                            plymouth = "Plymouth (UK)",
                            beijing = "Beijing (China)", 
                            india = "Pune (India)",
                            buenos_aires = "Buenos Aires (Argentina)",
                            auckland = "Auckland (New Zealand)",
                            turkey = "Malatya (Turkey)",
                            bandongo = "Bandongo (Rep. Congo)",
                            bayaka = "BaYaka (Rep. Congo)", 
                            uganda = "Nyabyeya (Uganda)"))
```
```{r}
# Population of the countries involved
(1394016000 + 1426093184 + 332639104	+ 214028304	+ 128649568 + 82017512 + 80159664 + 65761116 + 45479120 + 2630073	 + 43252968	 + 4925477	+ 17426624) /
8078229894 # proportion of world population

@@

@@

ggplot()+
  geom_point(data = ddata, aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
  geom_smooth(data = post, aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
  theme_minimal()+
  scale_fill_manual(name = "Community", values = colors)+
  scale_color_manual(name = "Community", values = colors)+
  labs(x = "Age", y="Imprecision")+
  theme(legend.position = "right")+
  facet_wrap(~continent, nrow = 2)#+guides(col = "none", fill = "none")
```

```{r}
ggsave("../visuals/dev.png", width = 12, height = 8, bg = "white")
```

@@

```{r}
plot_grid(
  plot_grid(am, eu, as,  nrow = 1),
  plot_grid(oc, af, NULL, rel_widths = c(0.975,1.45, 0.55), nrow = 1), nrow = 2, rel_heights = c(1,1.1) )
```
```{r}
ggsave("../visuals/dev_con.png", width = 14, height = 8, bg = "white", scale = 1)
```

@@

@@

>>>>

```{r}
library(tidyverse)
library(ggpubr)
library(ggthemes)
library(tidyboot)
library(maps)
library(brms)
library(cowplot)
library(png)
library(ggimage)
library(ggridges)
```

```{r}
data <- read_csv("../data/gafo-cc-clean-data.csv")%>%
  mutate(continent = ifelse(
    community %in% c("leipzig", "plymouth"), "Europe", 
    ifelse(
      community %in% c("akure", "hai||om", "khwe", "chimfunshi", "bandongo", "bayaka", "windhoek", "uganda"), "Africa",
      ifelse(community %in% c("stanford", "mexico", "buenos_aires"), "America",
             ifelse(community %in% c("india", "beijing", "turkey"), "Asia", "Oceania"))
    )
  ))%>%
  mutate(continent = factor(continent, levels = c("America", "Africa", "Europe", "Asia", "Oceania"), ordered = T))%>%
  mutate(community = recode(community,
                            akure = "Akure (Nigeria)",
                            leipzig = "Leipzig (Germany)",
                            `hai||om` = "Hai||om (Namibia)",
                            khwe = "Khwe (Namibia)",
                            windhoek = "Windhoek (Namibia)",
                            stanford = "Stanford (USA)",
                            chimfunshi = "Chimfunshi (Sambia)",
                            mexico = "Ocuilan (Mexico)",
                            plymouth = "Plymouth (UK)",
                            beijing = "Beijing (China)", 
                            india = "Pune (India)",
                            buenos_aires = "Buenos Aires (Argentina)",
                            auckland = "Auckland (New Zealand)",
                            turkey = "Malatya (Turkey)",
                            bandongo = "Bandongo (Rep. Congo)",
                            bayaka = "BaYaka (Rep. Congo)", 
                            uganda = "Nyabyeya (Uganda)"))

```
```{r}
# Population of the countries involved
(1394016000 + 1426093184 + 332639104	+ 214028304	+ 128649568 + 82017512 + 80159664 + 65761116 + 45479120 + 2630073	 + 43252968	 + 4925477	+ 17426624) /
8078229894 # proportion of world population

@@

```{r}
im <- readPNG("../visuals/gazemodel-cc-center.png")
im2 <- matrix(rgb(im[,,1],im[,,2],im[,,3], im[,,4] * 0.5), nrow=dim(im)[1])

sim_dat <- tibble(
  targetposition = factor(c(1:10)), 
  mean = c(550,350,225, 150 , 100, 100, 150,225,350,550),
  sd = c(seq(100,50, length.out = 5), seq(50, 100, length.out = 5)),
  col = c("no","no","no","no","yes","yes","no","no","no","no")
)%>%
  expand_grid(id = as.character(c(1:50)))%>%
  rowwise()%>%
  mutate(impr = rnorm(1, mean, sd))

ggplot(sim_dat, aes(x = targetposition, y= mean, col = col))+
  background_image(im2) + 
  geom_point(size = 3)+
  geom_jitter(aes(y = impr), alpha = 0.1, width = 0.1)+
  scale_color_manual(values = c("black", "firebrick"), guide = "none")+
  ylim(0, 1000)+
  labs(x = "Target position (binned)", y = "Imprecision")+
  theme_few()

ggsave("../visuals/target_position_model_center.png", width = 6.8, height = 4)

im3 <- readPNG("../visuals/gazemodel-cc-side.png")
im4 <- matrix(rgb(im3[,,1],im3[,,2],im3[,,3], im3[,,4] * 0.5), nrow=dim(im3)[1])

sim_dat2 <- tibble(
  targetposition = factor(c(1:10)), 
  mean = c(550,350,225, 150 , 100, 100, 150,225,350,550),
  sd = c(seq(100,50, length.out = 5), seq(50, 100, length.out = 5)),
  col = c("yes","no","no","no","no","no","no","no","no","yes")
)%>%
  expand_grid(id = as.character(c(1:50)))%>%
  rowwise()%>%
  mutate(impr = rnorm(1, mean, sd))

ggplot(sim_dat2, aes(x = targetposition, y= mean, col = col))+
  background_image(im4) + 
  geom_point(size = 3)+
  geom_jitter(aes(y = impr), alpha = 0.1, width = 0.1)+
  scale_color_manual(values = c("black", "firebrick"), guide = "none")+
  ylim(0, 1000)+
  labs(x = "Target position (binned)", y = "Imprecision")+
  theme_few()

ggsave("../visuals/target_position_model_edge.png", width = 6.8, height = 4)
```

@@

ndata_all <- ddata%>%
  distinct(ageinyears)

post_all <- fitted(bm_base, newdata = ndata_all, re_formula = NA)%>%
  as_tibble() %>%
  bind_cols(ndata_all)%>%
  mutate(ageinyears = ageinyears + min(data$ageinyears))

pagg_dev <- ggplot()+
  geom_point(data = ddata, aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
  #geom_smooth(data = post, aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .1, size = 0)+
  #geom_line(data = post, aes(x = ageinyears, y = Estimate, fill =community, col = community), stat = "identity", alpha = .4)+
  geom_smooth(data = post_all, aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5), stat = "identity", alpha = 0.5, col = "#555555", size = 1.5)+
  theme_few()+
    scale_x_continuous(limits = c(2,10))+
  scale_y_continuous(limits = c(0,1000))+
  scale_fill_manual(name = "Community", values = colors, guide = "none")+
  scale_color_manual(name = "Community", values = colors, guide = "none")+
  labs(x = "Age", y="Imprecision")+
  theme(legend.position = "right")
```

```{r}
pind <- ggplot()+ 
 geom_point(data = ddata, aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
  geom_smooth(data = post, aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
  theme_few()+
  scale_fill_manual(name = "Community", values = colors, guide = "none")+
  scale_color_manual(name = "color", values = colors, guide = "none")+
  labs(x = "Age", y="Imprecision")+
  scale_x_continuous(limits = c(2,10))+
  scale_y_continuous(limits = c(0,1000))+
  theme(legend.position = c(0.7, 0.9), legend.background = element_blank(),axis.title.x = element_blank(), axis.title.y = element_blank(), axis.ticks.y = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.text.y = element_blank())+
  facet_wrap(~community, nrow = 3)#+guides(col = "none", fill = "none")
```

```{r}
plot_grid(
  pagg_dev, pind, rel_widths = c(1,1.5), align = "h"
)
```

```{r}
ggsave("../visuals/dev2.png", width = 12, height = 4, bg = "white", scale = 1.25)
```

```{r}
tc_ind<- data%>%
  mutate(targetposition = factor(targetposition, levels = c(1:10)))%>%
  group_by(community, subjid, targetposition)%>%
  summarise(mean = mean(abs(clickdistfromtargetcenterx)))

tc_agg<- data%>%
  mutate(targetposition = factor(targetposition, levels = c(1:10)))%>%
  group_by(targetposition)%>%
  tidyboot_mean(col= abs(clickdistfromtargetcenterx))

tc_com<- data%>%
  mutate(targetposition = factor(targetposition, levels = c(1:10)))%>%
  group_by(community, targetposition)%>%
  tidyboot_mean(col= abs(clickdistfromtargetcenterx))

ptagg <- ggplot()+
  geom_jitter(data = tc_ind, aes(x = targetposition, y = mean, col = community), alpha = .05, height = 0, width = 0.2)+
  geom_pointrange(data =tc_agg, aes(x = targetposition, y = mean, ymin = ci_lower, ymax = ci_upper),pch = "-", col = "#555555", size = 3, stroke = 1.5, linewidth = 2)+
  #geom_pointrange(data =tc_com, aes(x = targetposition, y = mean, ymin = ci_lower, ymax = ci_upper, col = community),pch = 1, alpha = 0.2, position = position_dodge(width = 0.25))+
  labs(x = "Target position (binned)", y = "Imprecision")+
  scale_color_manual(name = "", guide = "none", values = colors)+
  ylim(0,1000)+
  theme_few()

ptind <- ggplot()+
  geom_pointrange(data =tc_com, aes(x = targetposition, y = mean, ymin = ci_lower, ymax = ci_upper, col = community),pch = "-", size = 1)+
  labs(x = "", y = "")+
  scale_color_manual(name = "", guide = "none", values = colors)+
  ylim(0,1000)+
  theme_few()+
  theme(legend.position = c(0.7, 0.9), legend.background = element_blank(),axis.title.x = element_blank(), axis.title.y = element_blank(), axis.ticks.y = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.text.y = element_blank())+
  facet_wrap(~community, nrow = 3)#+guides(col = "none", fill = "none")
```
```{r}
plot_grid(
  ptagg, ptind, rel_widths = c(1,1.5), align = "h"
)
```

```{r}
ggsave("../visuals/tc2.png", width = 12, height = 4, bg = "white", scale = 1.25)
```

```{r}
plot_grid(
plot_grid(
  pagg_dev, pind, rel_widths = c(1,1.5), align = "h", axis = "bt",labels = c("A", "B")
),
plot_grid(
  ptagg, ptind, rel_widths = c(1,1.5), align = "h", axis = "bt", labels = c("C", "D")
), nrow = 2, align = "v"
)
```
```{r}
ggsave("../visuals/fig2_alt2.png", width = 12, height = 8, bg = "white", scale = 1.25)
```

@@

```{r}
plot_grid(
  plot_grid(am, eu, as,  nrow = 1),
  plot_grid(oc, af, NULL, rel_widths = c(0.975,1.45, 0.55), nrow = 1), nrow = 2, rel_heights = c(1,1.1) )
```

```{r}
ggsave("../visuals/dev_con.png", width = 14, height = 8, bg = "white", scale = 1)
```

@@

# Inward clicks

```{r}

iclick = data%>%
  group_by(community, targetposition)%>%
  summarise(click_dist_mean = mean(clickdistfromtargetcenterx))
  mutate(click_dist_mean = ifelse(targetposition< 6, -click_dist_mean, click_dist_mean))

piclick <- data%>%
  mutate(fill1 = ifelse(targetcenterx < 960, -clickdistfromtargetcenterx, clickdistfromtargetcenterx), 
         fill = ifelse(fill1 < 0, "yes", "no"))%>%
  ggplot(aes(x = clickdistfromtargetcenterx, y = community))+
  #geom_density_ridges(data = .%>%filter(fill == "yes"), alpha = 0.5, col = NA, fill = "#85AD00",bandwidth = 200)+
  #geom_density_ridges(data = .%>%filter(fill == "no"), alpha = 0.5, col = NA, fill = "grey",bandwidth = 200)+
  geom_density_ridges(alpha = .75,  bandwidth = 200, fill = "grey", col = "white")+
  geom_vline(xintercept = 0, lty = 1, size = 1)+
  facet_grid(~factor(targetposition))+
  labs(x = "Click distance from target", y = "")+
  scale_x_continuous(breaks = c(0), limits = c(-1500, 1500))+
  scale_y_discrete(limits=rev)+
  #scale_fill_manual(values = c("grey","#85AD00"))+
  scale_color_manual(name = "", guide = "none", values = colors)+
  geom_point(data = iclick, aes(x = click_dist_mean, y = community), col = "firebrick", size = 1, stroke = 1)+
  theme_few()
```

```{r}
plot_grid(
plot_grid(
  pagg_dev, pind, rel_widths = c(1,1.5), align = "h", axis = "bt",labels = c("A", "B")
),
plot_grid(
  ptagg, ptind, rel_widths = c(1,1.5), align = "h", axis = "bt", labels = c("C", "D")
), 
piclick,
nrow = 3, align = "v", rel_heights = c(1,1, 0.6)
)
```

```{r}
ggsave("../visuals/fig2_alt3.png", width = 12, height = 10, bg = "white", scale = 1.4)
```

@@

```{r}
gWorld <- world%>%
  filter(region != "Antarctica")%>%
  mutate(fill = ifelse(region %in% c("Turkey", "Germany", "Kenya"), "out", "in"))%>% 
  filter(! long > 180)
```

```{r}
ggplot(data = gWorld%>%filter(! long  < -30, long < 60,  lat > -40, lat < 70 ), mapping = aes(x = long, y = lat, group = group)) + 
  coord_map("moll")+
  geom_polygon(aes(fill = fill), col = NA, linewidth = 0) +
  scale_fill_manual(breaks = c("out", "in"), values = c( "black", "#f2f2f2"), guide = "none")+
  plain

library(rworldmap)
cont <- map_data(coastsCoarse)
plot(coastsCoarse)
```

```{r}
ggsave("../../../../../../Desktop/map.png", width = 4, height = 4, scale = 1.3)
```

```{r}
gWorld2 <- world%>%
  filter(region != "Antarctica")%>%
  mutate(fill = ifelse(region %in% c("Turkey", "Germany", "Kenya", "USA", "Mexico", "Argentina", "Colombia", "Morocco", "Nigeria", "Namibia", "India", "China", "Malaysia", "Australia", "Zambia", "Japan", "Spain", "UK", "Republic of Congo", "Sweden", "Turkmenistan"), "out", "in"))%>% 
  filter(! long > 180)
```

```{r}
ggplot(data = gWorld2, mapping = aes(x = long, y = lat, group = group)) + 
  coord_map("moll")+
  geom_polygon(aes(fill = fill), col = NA, linewidth = 0) +
  scale_fill_manual(breaks = c("out", "in"), values = c( "#DBD56E", "grey"), guide = "none")+
  plain
```

```{r}
ggsave("../../../../../../Desktop/map2.png", width = 12, height = 8, scale = 1)
```
